Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-14 doc/JFLA2022/paper.tex
pass over conclusion to place Gaia material in correct place

The Gaia project by Jos\'e Grimm aimed to formalize mathematics in Coq in the style of Nicolas Bourbaki. The formalization of the first book in the Elements of Mathematics series by Bourbaki, on the theory of sets, was initially described in a technical report in July 2009~\cite{Grimm2009a}. Grimm then wrote (and continually updated) technical reports describing the formalization of Bourbaki's two subsequent books~\cite{Grimm2009b,Grimm2016} and additional topics in number theory~\cite{grimm:hal-00911710,Grimm2014}, before he passed away in 2019.

@@

We plan to extend our libraries in two main directions.

The \gaia project~\cite{Gaia}, also maintained on \community, contains a development by José Grimm~\cite{grimm:hal-00911710},  dedicated  to the implementation in \coq (SSReflect) of books from  Bourbaki's Elements of Mathematics. The set theory underpinning \gaia is derived from an earlier development by Carlos Simpson~\cite{Simpson2004,CatsZFCContrib}. \gaia contains data structures which are compatible with our ordinal notations.
Our plan is to build a  bridge between  the combinatorial results of \Hydras and the set-theoretic content of \gaia, and make possible the transfer of theorems between both libraries.
We aim also to write in \coq a formal proof of the original statement of Theorem~\ref{kp:thm2}, using O'Connor's formalization of Peano Arithmetic~\cite{Goedel}.

>>>>

The Gaia project by Jos\'e Grimm aimed to formalize mathematics in Coq in the style of Nicolas Bourbaki. The formalization of the first book in the Elements of Mathematics series by Bourbaki, on the theory of sets, was initially described in a technical report in July 2009~\cite{Grimm2009a}. The set-theoretic axioms and basic definitions in \gaia were derived from an earlier development by Carlos Simpson~\cite{Simpson2004,CatsZFCContrib}. Grimm then wrote (and continually updated) technical reports describing the formalization of Bourbaki's two subsequent books~\cite{Grimm2009b,Grimm2016} and additional topics in number theory~\cite{grimm:hal-00911710,Grimm2014}, before he passed away in 2019.

@@

We plan to extend \Hydras in two main directions. Firstly, we plan to build a bridge between the combinatorial results of \Hydras and the set-theoretic content of \gaia, and make possible the transfer of many interesting theorems between the two packages. Secondly, we aim to write a formal proof in \coq of the original statement of Theorem~\ref{kp:thm2}, using O'Connor's formalization of Peano Arithmetic~\cite{Goedel}.
